---
title: "DGS - Questionnaires for Experimental Group"
author: "Rachael Martin"
date: "`r Sys.Date()`"
output:
  tufte::tufte_html: 
    toc: true
---

# Notes

Cases whereby participants were missing data for a single item were overcome through use of adjusted means (via rowMeans function)

Cases whereby participants are missing data for an entire measure and may require imputation are decided on by the individual researcher conducting analysis

The SMA is not scored as our adapted version is one single variable

# Import

```{r}
library(haven)
library(data.table)
library(JWileymisc)
library(psych)

db <- as.data.table(read.csv("experimental_data_COPYforR.csv"))
```
# Converting all to numeric
```{r}
## SCS
cols_reversed <- c("SCS.R.1_3", "SCS.R.1_6", "SCS.R.1_7", "SCS.R.1_9", "SCS.R.1_11", "SCS.R.1_13", "SCS.R.1_15", "SCS.R.1_17", "SCS.R.1_18", "SCS.R.1_20")
cols_nonreversed <- c("SCS.R.1_1", "SCS.R.1_2", "SCS.R.1_4", "SCS.R.1_5", "SCS.R.1_8", "SCS.R.1_10", "SCS.R.1_12", "SCS.R.1_14", "SCS.R.1_16", "SCS.R.1_19")

# Reverse columns
db[, (cols_reversed) := lapply(.SD, function(x) 5 - as.numeric(x)), .SDcols = cols_reversed]

# Convert non-reversed columns to numeric
db[, (cols_nonreversed) := lapply(.SD, as.numeric), .SDcols = cols_nonreversed]

cols_to_reverse <- c("SCS.R.2_3", "SCS.R.2_6", "SCS.R.2_7", "SCS.R.2_9", "SCS.R.2_11", 
                     "SCS.R.2_13", "SCS.R.2_15", "SCS.R.2_17", "SCS.R.2_18", "SCS.R.2_20")
                     
db[, (cols_to_reverse) := lapply(.SD, function(x) 5 - as.numeric(x)), .SDcols = cols_to_reverse]

cols_to_numeric <- c("SCS.R.2_1", "SCS.R.2_2", "SCS.R.2_4", "SCS.R.2_5", "SCS.R.2_8", 
                     "SCS.R.2_10", "SCS.R.2_12", "SCS.R.2_14", "SCS.R.2_16", "SCS.R.2_19")

db[, (cols_to_numeric) := lapply(.SD, as.numeric), .SDcols = cols_to_numeric]

## SSES

db$SSES.1 <- as.numeric(db$SSES.1)
db$SSES.2 <- as.numeric(db$SSES.2)
db$SSES.3 <- as.numeric(db$SSES.3)
db$SSES.4 <- as.numeric(db$SSES.4)
db$SSES.5 <- as.numeric(db$SSES.5)
db$SSES.6 <- as.numeric(db$SSES.6)
db$SSES.7 <- as.numeric(db$SSES.7)

## SSGLBT

db$SSGLBT.1 <- as.numeric(db$SSGLBT.1)
db$SSGLBT.2 <- as.numeric(db$SSGLBT.2)
db$SSGLBT.3 <- as.numeric(db$SSGLBT.3)
db$SSGLBT.4 <- as.numeric(db$SSGLBT.4)

## DASS21
cols_to_transform <- paste0("DASS.21_", c("Current", "Puberty"), "_", 1:21)

db[, (cols_to_transform) := lapply(.SD, function(x) as.numeric(x) - 1), .SDcols = cols_to_transform]

#MSPSS puberty
db[, paste0("MSPSS.1.1_", 1:7)] <- lapply(db[, paste0("MSPSS.1.1_", 1:7)], as.numeric)
db[, paste0("MSPSS.2.1_", 1:6)] <- lapply(db[, paste0("MSPSS.2.1_", 1:6)], as.numeric)

#MSPSS now
db[, paste0("MSPSS.1.2_", 1:7)] <- lapply(db[, paste0("MSPSS.1.2_", 1:7)], as.numeric)
db[, paste0("MSPSS.2.2_", 1:6)] <- lapply(db[, paste0("MSPSS.2.2_", 1:6)], as.numeric)

#FCS
cols <- c("FCS.1.1_1", "FCS.1.2_1", "FCS.2.1_1", "FCS.2.1_2", "FCS.2.1_3", 
          "FCS.2.1_4", "FCS.3.1_1", "FCS.3.1_2", "FCS.3.1_3", "FCS.3.1_4", "FCS.3.1_5")

db[, (cols) := lapply(.SD, as.numeric), .SDcols = cols]

## EDS
db[, c("EDS.1_1", "EDS.1_2", "EDS.1_3", "EDS.1_4", "EDS.1_5", "EDS.1_6", "EDS.1_7", "EDS.1_8", "EDS.1_9")] <- lapply(db[, c("EDS.1_1", "EDS.1_2", "EDS.1_3", "EDS.1_4", "EDS.1_5", "EDS.1_6", "EDS.1_7", "EDS.1_8", "EDS.1_9")],as.numeric)

## BloomS
db[, c("BloomS_1", "BloomS_2", "BloomS_3", "BloomS_4", "BloomS_5")] <- lapply(db[, c("BloomS_1", "BloomS_2", "BloomS_3", "BloomS_4", "BloomS_5")],as.numeric)

## PDS
db[, c("Retro_PDS.1_1", "Retro_PDS.1_2", "Retro_PDS.1_3", "Retro_PDS.1_4", "Retro_PDS.1_5", "Retro_PDS.1_6", "Retro_PDS.1_7")] <- lapply(db[, c("Retro_PDS.1_1", "Retro_PDS.1_2", "Retro_PDS.1_3", "Retro_PDS.1_4", "Retro_PDS.1_5", "Retro_PDS.1_6", "Retro_PDS.1_7")],as.numeric)

## CTQ
db[, c("CTQ.1_1", "CTQ.1_2", "CTQ.1_3", "CTQ.1_4", "CTQ.1_5", "CTQ.1_6", "CTQ.1_7", "CTQ.1_8", "CTQ.1_9", "CTQ.1_10", "CTQ.1_11", "CTQ.1_12", "CTQ.1_13", "CTQ.1_14","CTQ.1_15", "CTQ.1_16", "CTQ.1_17", "CTQ.1_18", "CTQ.1_19", "CTQ.1_20", "CTQ.1_21", "CTQ.1_22", "CTQ.1_23", "CTQ.1_24", "CTQ.1_25", "CTQ.1_26", "CTQ.1_27", "CTQ.1_28", "CTQ.1_29", "CTQ.1_30", "CTQ.1_31", "CTQ.1_32"  )] <- lapply(db[, c("CTQ.1_1", "CTQ.1_2", "CTQ.1_3", "CTQ.1_4", "CTQ.1_5", "CTQ.1_6", "CTQ.1_7", "CTQ.1_8", "CTQ.1_9", "CTQ.1_10", "CTQ.1_11", "CTQ.1_12", "CTQ.1_13", "CTQ.1_14","CTQ.1_15", "CTQ.1_16", "CTQ.1_17", "CTQ.1_18", "CTQ.1_19", "CTQ.1_20", "CTQ.1_21", "CTQ.1_22", "CTQ.1_23", "CTQ.1_24", "CTQ.1_25", "CTQ.1_26", "CTQ.1_27", "CTQ.1_28", "CTQ.1_29", "CTQ.1_30", "CTQ.1_31", "CTQ.1_32"  )],as.numeric)

## DHEQ
cols <- c("DHEQ_GE.Puberty_1", "DHEQ_GE.Puberty_2", "DHEQ_GE.Puberty_3", "DHEQ_GE.Puberty_4", "DHEQ_GE.Puberty_5", "DHEQ_GE.Puberty_6")
db[, (cols) := lapply(.SD, as.numeric), .SDcols = cols]
columns_to_convert <- c("DHEQ_HD.Puberty_1", "DHEQ_HD.Puberty_2", "DHEQ_HD.Puberty_3", 
                        "DHEQ_HD.Puberty_4", "DHEQ_HD.Puberty_5", "DHEQ_HD.Puberty_6", 
                        "DHEQ_Vic.Puberty_1", "DHEQ_Vic.Puberty_2", "DHEQ_Vic.Puberty_3", 
                        "DHEQ_Vic.Puberty_4", "DHEQ_Vig.Puberty_1", "DHEQ_Vig.Puberty_2", 
                        "DHEQ_Vig.Puberty_3", "DHEQ_Vig.Puberty_4", "DHEQ_Vig.Puberty_5", 
                        "DHEQ_Vig.Puberty_6", "DHEQ_FO.Puberty_1", "DHEQ_FO.Puberty_2", 
                        "DHEQ_FO.Puberty_3", "DHEQ_FO.Puberty_4", "DHEQ_FO.Puberty_5", 
                        "DHEQ_FO.Puberty_6", "DHEQ_VT.Puberty_1", "DHEQ_VT.Puberty_2", 
                        "DHEQ_VT.Puberty_3", "DHEQ_VT.Puberty_4", "DHEQ_VT.Puberty_5", 
                        "DHEQ_VT.Puberty_6", "DHEQ_I.Puberty_1", "DHEQ_I.Puberty_2", 
                        "DHEQ_I.Puberty_3", "DHEQ_I.Puberty_4")
db[, (columns_to_convert) := lapply(.SD, as.numeric), .SDcols = columns_to_convert]

## YASB
db[, c("YASB_1", "YASB_2", "YASB_3", "YASB_4", "YASB_5", "YASB_6", "YASB_7", "YASB_8", "YASB_9", "YASB_10", "YASB_11", "YASB_12", "YASB_13", "YASB_14")] <- lapply(db[, c("YASB_1", "YASB_2", "YASB_3", "YASB_4", "YASB_5", "YASB_6", "YASB_7", "YASB_8", "YASB_9", "YASB_10", "YASB_11", "YASB_12", "YASB_13", "YASB_14")],as.numeric)

## TCS
db[, c("TCS.1_1", "TCS.1_2", "TCS.1_3", "TCS.1_4", "TCS.1_5", "TCS.2_1", "TCS.2_2", "TCS.2_3", "TCS.2_4", "TCS.2_5")] <- lapply(db[, c("TCS.1_1", "TCS.1_2", "TCS.1_3", "TCS.1_4", "TCS.1_5", "TCS.2_1", "TCS.2_2", "TCS.2_3", "TCS.2_4", "TCS.2_5")],as.numeric)

## CTSM
db[, c("CTSM.1.1_1", "CTSM.1.1_2", "CTSM.1.1_3", "CTSM.1.1_4", "CTSM.1.1_5", "CTSM.1.1_6", "CTSM.1.2_1", "CTSM.1.2_2", "CTSM.1.2_3", "CTSM.1.2_4", "CTSM.1.2_5", "CTSM.1.2_6")] <- lapply(db[, c("CTSM.1.1_1", "CTSM.1.1_2", "CTSM.1.1_3", "CTSM.1.1_4", "CTSM.1.1_5", "CTSM.1.1_6", "CTSM.1.2_1", "CTSM.1.2_2", "CTSM.1.2_3", "CTSM.1.2_4", "CTSM.1.2_5", "CTSM.1.2_6")],as.numeric)

## COS
db[, c("COS.1.1_1", "COS.1.1_2", "COS.1.1_3", "COS.1.2_1", "COS.1.2_2", "COS.1.2_3")] <- lapply(db[, c("COS.1.1_1", "COS.1.1_2", "COS.1.1_3", "COS.1.2_1", "COS.1.2_2", "COS.1.2_3")], as.numeric)

```


# Missing data

```{r}
# Check for missing values in SCSR (puberty)
missing_SCS1 <- is.na(db$SCSR1_Total)
sum(missing_SCS1)

# Check for missing values in SCSR (now)
missing_SCS2 <- is.na(db$SCSR2_Total)
sum(missing_SCS2)

# Check for missing values in SSES_Avg
missing_SSES <- is.na(db$SSES_Avg)
sum(missing_SSES)

# Check for missing values in SSGBLT_Avg
missing_SSGBLT <- is.na(db$SSGBLT_Avg)
sum(missing_SSGBLT)

# Check for missing values in DASS21 (now)
missing_DASS21_CTotal <- is.na(db$DASS21_CTotal)
sum(missing_DASS21_CTotal)

# Check for missing values in DASS21 (puberty)
missing_DASS21_PTotal <- is.na(db$DASS21_PTotal)
sum(missing_DASS21_PTotal)

# Check for missing values in MSPSS (puberty)
missing_MSPSS_P_TOTAL <- is.na(db$MSPSS_P_TOTAL)
sum(missing_MSPSS_P_TOTAL)

# Check for missing values in MSPSS (now)
missing_MSPSS_C_TOTAL <- is.na(db$MSPSS_C_TOTAL)
sum(missing_MSPSS_C_TOTAL)

# Check for missing values in FCS_Avg
missing_FCS <- is.na(db$FCS_Avg)
sum(missing_FCS)

# Check for missing values in EDS_Total
missing_EDS_Total <- is.na(db$EDS_Total)
sum(missing_EDS_Total)

# Check for missing values in BloomS_Average
missing_BloomS_Average <- is.na(db$BloomS_Average)
sum(missing_BloomS_Average)

# Check for missing values in PDS_Sum
missing_PDS_Sum <- is.na(db$PDS_Sum)
sum(missing_PDS_Sum)

# Check for missing values in CTQ_Minimise
missing_CTQ_Minimise <- is.na(db$CTQ_Minimise)
sum(missing_CTQ_Minimise)

# Check for missing values in CTQ_PhysicalNeglect
missing_CTQ_PhysicalNeglect <- is.na(db$CTQ_PhysicalNeglect)
sum(missing_CTQ_PhysicalNeglect)

# Check for missing values in CTQ_EmotionNeglect
missing_CTQ_EmotionNeglect <- is.na(db$CTQ_EmotionNeglect)
sum(missing_CTQ_EmotionNeglect)

# Check for missing values in CTQ_SexAbuse
missing_CTQ_SexAbuse <- is.na(db$CTQ_SexAbuse)
sum(missing_CTQ_SexAbuse)

# Check for missing values in CTQ_PhysicalAbuse
missing_CTQ_PhysicalAbuse <- is.na(db$CTQ_PhysicalAbuse)
sum(missing_CTQ_PhysicalAbuse)

# Check for missing values in CTQ_EmotionAbuse
missing_CTQ_EmotionAbuse <- is.na(db$CTQ_EmotionAbuse)
sum(missing_CTQ_EmotionAbuse)

# Check for missing values in DHEQ_V1_HD_Avg
missing_DHEQ_V1_HD_Avg <- is.na(db$DHEQ_V1_HD_Avg)
sum(missing_DHEQ_V1_HD_Avg)

# Check for missing values in DHEQ_V1_GE_Avg
missing_DHEQ_V1_GE_Avg <- is.na(db$DHEQ_V1_GE_Avg)
sum(missing_DHEQ_V1_GE_Avg)

# Check for missing values in DHEQ_V1_Vic_Avg
missing_DHEQ_V1_Vic_Avg <- is.na(db$DHEQ_V1_Vic_Avg)
sum(missing_DHEQ_V1_Vic_Avg)

# Check for missing values in DHEQ_V1_Vig_Avg
missing_DHEQ_V1_Vig_Avg <- is.na(db$DHEQ_V1_Vig_Avg)
sum(missing_DHEQ_V1_Vig_Avg)

# Check for missing values in DHEQ_V1_FO_Avg
missing_DHEQ_V1_FO_Avg <- is.na(db$DHEQ_V1_FO_Avg)
sum(missing_DHEQ_V1_FO_Avg)

# Check for missing values in DHEQ_V1_VT_Avg
missing_DHEQ_V1_VT_Avg <- is.na(db$DHEQ_V1_VT_Avg)
sum(missing_DHEQ_V1_VT_Avg)

# Check for missing values in DHEQ_V1_I_Avg
missing_DHEQ_V1_I_Avg <- is.na(db$DHEQ_V1_I_Avg)
sum(missing_DHEQ_V1_I_Avg)

# Check for missing values in YASB_RelAg
missing_YASB_RelAg <- is.na(db$YASB_RelAg)
sum(missing_YASB_RelAg)

# Check for missing values in YASB_SocAg
missing_YASB_SocAg <- is.na(db$YASB_SocAg)
sum(missing_YASB_SocAg)

# Check for missing values in YASB_Mat
missing_YASB_Mat <- is.na(db$YASB_Mat)
sum(missing_YASB_Mat)
```


# Social connectedness scale - revised

```{r}
## scoring - now
db[, SCSR2_Total := rowMeans(.SD, na.rm = TRUE)*20,
   .SDcols = c("SCS.R.2_1", "SCS.R.2_2", "SCS.R.2_3", "SCS.R.2_4", "SCS.R.2_5", "SCS.R.2_6", "SCS.R.2_7", "SCS.R.2_8", "SCS.R.2_9", "SCS.R.2_10", "SCS.R.2_11", "SCS.R.2_12", "SCS.R.2_13", "SCS.R.2_14", "SCS.R.2_15", "SCS.R.2_16", "SCS.R.2_17", "SCS.R.2_18", "SCS.R.2_19", "SCS.R.2_20")]

# Compute Cronbach's alpha
SCS2_alpha <- alpha(db[, c("SCS.R.2_1", "SCS.R.2_2", "SCS.R.2_3", "SCS.R.2_4", "SCS.R.2_5", "SCS.R.2_6", "SCS.R.2_7", "SCS.R.2_8", "SCS.R.2_9", "SCS.R.2_10",          "SCS.R.2_11", "SCS.R.2_12", "SCS.R.2_13", "SCS.R.2_14", "SCS.R.2_15",          "SCS.R.2_16", "SCS.R.2_17", "SCS.R.2_18", "SCS.R.2_19", "SCS.R.2_20")])

# View the results
print(SCS2_alpha$total)

## summary now
summary(db$SCSR2_Total)
sd(db$SCSR2_Total)

## scoring - puberty


db[, SCSR1_Total := rowMeans(.SD, na.rm = TRUE)*20,
   .SDcols = c("SCS.R.1_1", "SCS.R.1_2", "SCS.R.1_3", "SCS.R.1_4", "SCS.R.1_5", "SCS.R.1_6", "SCS.R.1_7", "SCS.R.1_8", "SCS.R.1_9", "SCS.R.1_10", "SCS.R.1_11", "SCS.R.1_12", "SCS.R.1_13", "SCS.R.1_14", "SCS.R.1_15", "SCS.R.1_16", "SCS.R.1_17", "SCS.R.1_18", "SCS.R.1_19", "SCS.R.1_20")]

db$SCSR1_Total <- as.numeric(db$SCSR1_Total)

# Cronbachs alpha
SCS1_alpha <- alpha(db[, c("SCS.R.1_1", "SCS.R.1_2", "SCS.R.1_3", "SCS.R.1_4", "SCS.R.1_5", "SCS.R.1_6", "SCS.R.1_7", "SCS.R.1_8", "SCS.R.1_9", "SCS.R.1_10", "SCS.R.1_11", "SCS.R.1_12", "SCS.R.1_13", "SCS.R.1_14", "SCS.R.1_15", "SCS.R.1_16", "SCS.R.1_17", "SCS.R.1_18", "SCS.R.1_19", "SCS.R.1_20")])

print(SCS1_alpha$total)

## summary puberty
summary(db$SCSR1_Total)
sd(db$SCSR1_Total, na.rm = TRUE)

```

# Supportive School Environment Scale
```{r}
## remove 'prefer not to say'
db[, SSES.2 := ifelse(SSES.2 == 3, NA, SSES.2)]
db[, SSES.3 := ifelse(SSES.2 == 4, NA, SSES.3)]
db[, SSES.4 := ifelse(SSES.4 == 4, NA, SSES.4)]


## reversal
db[, SSES.3 := (5 - SSES.3)]
db[, SSES.4 := (4 - SSES.4)]
db[, SSES.6 := (6 - SSES.6)]

## average for SSES
db[, SSES_Avg := rowMeans(.SD, na.rm = TRUE), .SDcols = c("SSES.1", "SSES.2", "SSES.3", "SSES.4", "SSES.5", "SSES.6", "SSES.7")]

## alpha
SSES_alpha <- alpha(db[, c("SSES.1", "SSES.2", "SSES.3", "SSES.4", "SSES.5", "SSES.6", "SSES.7")])

print(SSES_alpha$total)

## summary

summary(db$SSES_Avg)
sd(db$SSES_Avg, na.rm = TRUE)

```

# Supportive School GLBT

```{r}
##reverse scoring
db[, SSGLBT.3 := 6 - SSGLBT.3]
db[, SSGLBT.4 := 6 - SSGLBT.4]

## alpha
SSGLBT_alpha <- alpha(db[, c("SSGLBT.1", "SSGLBT.2", "SSGLBT.3", "SSGLBT.4")])

print(SSGLBT_alpha$total)


## create average
db[, SSGLBT_Avg := rowMeans(.SD, na.rm = TRUE), .SDcols = c("SSGLBT.1", "SSGLBT.2", "SSGLBT.3", "SSGLBT.4")]

## summary

summary(db$SSGLBT_Avg)
sd(db$SSGLBT_Avg, na.rm = TRUE)

```


# DASS-21
```{r}

## puberty alpha
DASS_P_alpha <- alpha(db[, c("DASS.21_Puberty_1", "DASS.21_Puberty_2", "DASS.21_Puberty_3", "DASS.21_Puberty_4", "DASS.21_Puberty_5", "DASS.21_Puberty_6", "DASS.21_Puberty_7", "DASS.21_Puberty_8", "DASS.21_Puberty_9", "DASS.21_Puberty_10", "DASS.21_Puberty_11", "DASS.21_Puberty_12", "DASS.21_Puberty_13", "DASS.21_Puberty_14", "DASS.21_Puberty_15", "DASS.21_Puberty_16", "DASS.21_Puberty_17", "DASS.21_Puberty_18", "DASS.21_Puberty_19", "DASS.21_Puberty_20", "DASS.21_Puberty_21")])

print(DASS_P_alpha$total)

## depression puberty alpha

DASS_PD_alpha <- alpha(db[, c("DASS.21_Puberty_3", "DASS.21_Puberty_5", "DASS.21_Puberty_10", "DASS.21_Puberty_13", "DASS.21_Puberty_16", "DASS.21_Puberty_17", "DASS.21_Puberty_21")])

print(DASS_PD_alpha$total)

## current alpha
DASS_C_alpha <- alpha(db[, c("DASS.21_Current_1", "DASS.21_Current_2", "DASS.21_Current_3", "DASS.21_Current_4", "DASS.21_Current_5", "DASS.21_Current_6", "DASS.21_Current_7", "DASS.21_Current_8", "DASS.21_Current_9", "DASS.21_Current_10", "DASS.21_Current_11", "DASS.21_Current_12", "DASS.21_Current_13", "DASS.21_Current_14", "DASS.21_Current_15", "DASS.21_Current_16", "DASS.21_Current_17", "DASS.21_Current_18", "DASS.21_Current_19", "DASS.21_Current_20", "DASS.21_Current_21")])

print(DASS_C_alpha$total)

## depression current alpha
DASS_CD_alpha <- alpha(db[, c("DASS.21_Current_3", "DASS.21_Current_5", "DASS.21_Current_10", "DASS.21_Current_13", "DASS.21_Current_16", "DASS.21_Current_17", "DASS.21_Current_21")])

print(DASS_CD_alpha$total)

## depression - now
db[, DASS21_CDepression1 := rowMeans(.SD, na.rm = TRUE)*7,
     .SDcols = c("DASS.21_Current_3", "DASS.21_Current_5", "DASS.21_Current_10", "DASS.21_Current_13", "DASS.21_Current_16", "DASS.21_Current_17", "DASS.21_Current_21")]

db[, DASS21_CDepressionFINAL := DASS21_CDepression1*2]

summary(db$DASS21_CDepressionFINAL)
sd(db$DASS21_CDepressionFINAL, na.rm = TRUE)
## anxiety - now
db[, DASS21_CAnxiety1 := rowMeans(.SD, na.rm = TRUE)*7,
     .SDcols = c("DASS.21_Current_2", "DASS.21_Current_4", "DASS.21_Current_7", "DASS.21_Current_9", "DASS.21_Current_15", "DASS.21_Current_19", "DASS.21_Current_20")]

db[, DASS21_CAnxietyFINAL := DASS21_CAnxiety1*2]

## stress - now
db[, DASS21_CStress1 := rowMeans(.SD, na.rm = TRUE)*7,
     .SDcols = c("DASS.21_Current_1", "DASS.21_Current_6", "DASS.21_Current_8", "DASS.21_Current_11", "DASS.21_Current_12", "DASS.21_Current_14", "DASS.21_Current_18")]

db[, DASS21_CStressFINAL := DASS21_CStress1*2]

## total - now
db[, DASS21_CTotal := DASS21_CStressFINAL + DASS21_CAnxietyFINAL + DASS21_CDepressionFINAL]

## depression - puberty
db[, DASS21_PDepression1 := rowMeans(.SD, na.rm = TRUE)*7,
     .SDcols = c("DASS.21_Puberty_3", "DASS.21_Puberty_5", "DASS.21_Puberty_10", "DASS.21_Puberty_13", "DASS.21_Puberty_16", "DASS.21_Puberty_17", "DASS.21_Puberty_21")]

db[, DASS21_PDepressionFINAL := DASS21_PDepression1*2]

summary(db$DASS21_PDepressionFINAL)
sd(db$DASS21_PDepressionFINAL, na.rm = TRUE)
## anxiety - puberty
db[, DASS21_PAnxiety1 := rowMeans(.SD, na.rm = TRUE)*7,
     .SDcols = c("DASS.21_Puberty_2", "DASS.21_Puberty_4", "DASS.21_Puberty_7", "DASS.21_Puberty_9", "DASS.21_Puberty_15", "DASS.21_Puberty_19", "DASS.21_Puberty_20")]

db[, DASS21_PAnxietyFINAL := DASS21_PAnxiety1*2]

## stress - puberty
db[, DASS21_PStress1 := rowMeans(.SD, na.rm = TRUE)*7,
     .SDcols = c("DASS.21_Puberty_1", "DASS.21_Puberty_6", "DASS.21_Puberty_8", "DASS.21_Puberty_11", "DASS.21_Puberty_12", "DASS.21_Puberty_14", "DASS.21_Puberty_18")]

db[, DASS21_PStressFINAL := DASS21_PStress1*2]

## total - puberty
db[, DASS21_PTotal := DASS21_PStressFINAL + DASS21_PAnxietyFINAL + DASS21_PDepressionFINAL]

## summary - puberty 
summary(db$DASS21_PTotal)
sd(db$DASS21_PTotal, na.rm = TRUE)

## summary - now 
summary(db$DASS21_CTotal)
sd(db$DASS21_CTotal, na.rm = TRUE)
```
# MSPSS
```{r}
## puberty alpha
MSPSS_P_alpha <- alpha(db[, c("MSPSS.1.1_1", "MSPSS.1.1_2", "MSPSS.1.1_3", "MSPSS.1.1_4", "MSPSS.1.1_5", "MSPSS.1.1_6", "MSPSS.1.1_7", "MSPSS.2.1_1", "MSPSS.2.1_2", "MSPSS.2.1_3", "MSPSS.2.1_4", "MSPSS.2.1_5", "MSPSS.2.1_6")])

print(MSPSS_P_alpha$total)

## current alpha
MSPSS_C_alpha <- alpha(db[, c("MSPSS.1.2_1", "MSPSS.1.2_2", "MSPSS.1.2_3", "MSPSS.1.2_4", "MSPSS.1.2_5", "MSPSS.1.2_6", "MSPSS.1.2_7", "MSPSS.2.2_1", "MSPSS.2.2_2", "MSPSS.2.2_3", "MSPSS.2.2_4", "MSPSS.2.2_5", "MSPSS.2.2_6")])

print(MSPSS_C_alpha$total)


## scoring puberty

## significant other subscale
db[, MSPSS_P_SO := rowMeans(.SD, na.rm = TRUE), .SDcols = c("MSPSS.1.1_1", "MSPSS.1.1_2", "MSPSS.1.1_5", "MSPSS.2.1_4")]

## family subscale
db[, MSPSS_P_Fa := rowMeans(.SD, na.rm = TRUE), .SDcols = c("MSPSS.1.1_3", "MSPSS.1.1_4", "MSPSS.2.1_2", "MSPSS.2.1_5")]

## friends subscale
db[, MSPSS_P_Fr := rowMeans(.SD, na.rm = TRUE), .SDcols = c("MSPSS.1.1_6", "MSPSS.2.1_1", "MSPSS.2.1_3", "MSPSS.2.1_6")]

## total
db[, MSPSS_P_TOTAL := rowMeans(.SD, na.rm = TRUE), .SDcols = c("MSPSS.1.1_1", "MSPSS.1.1_2", "MSPSS.1.1_3", "MSPSS.1.1_4", "MSPSS.1.1_5", "MSPSS.1.1_6", "MSPSS.2.1_1", "MSPSS.2.1_2", "MSPSS.2.1_3", "MSPSS.2.1_4", "MSPSS.2.1_5", "MSPSS.2.1_6")]

## scoring now

## significant other subscale
db[, MSPSS_C_SO := rowMeans(.SD, na.rm = TRUE), .SDcols = c("MSPSS.1.2_1", "MSPSS.1.2_2", "MSPSS.1.2_5", "MSPSS.1.2_4")]

## family subscale
db[, MSPSS_C_Fa := rowMeans(.SD, na.rm = TRUE), .SDcols = c("MSPSS.1.2_3", "MSPSS.1.2_4", "MSPSS.2.2_2", "MSPSS.2.2_5")]

## friends subscale
db[, MSPSS_C_Fr := rowMeans(.SD, na.rm = TRUE), .SDcols = c("MSPSS.1.2_6", "MSPSS.2.2_1", "MSPSS.2.2_3", "MSPSS.2.2_6")]

## total
db[, MSPSS_C_TOTAL := rowMeans(.SD, na.rm = TRUE), .SDcols = c("MSPSS.1.2_1", "MSPSS.1.2_2", "MSPSS.1.2_3", "MSPSS.1.2_4", "MSPSS.1.2_5", "MSPSS.1.2_6", "MSPSS.2.2_1", "MSPSS.2.2_2", "MSPSS.2.2_3", "MSPSS.2.2_4", "MSPSS.2.2_5", "MSPSS.2.2_6")]

## summary - now 
summary(db$MSPSS_C_TOTAL)
sd(db$MSPSS_C_TOTAL, na.rm = TRUE)

## summary - puberty 
summary(db$MSPSS_P_TOTAL, na.rm = TRUE)
sd(db$MSPSS_P_TOTAL, na.rm = TRUE)

```
# FCS
```{r}
## scoring puberty 
db[, FCS_PAvg := rowMeans(.SD, na.rm = TRUE), .SDcols = c("FCS.3.1_1", "FCS.3.1_2", "FCS.3.1_3", "FCS.3.1_4", "FCS.3.1_5")]

## puberty alpha
FCS_Palpha <- alpha(db[, c("FCS.3.1_1", "FCS.3.1_2", "FCS.3.1_3", "FCS.3.1_4", "FCS.3.1_5")])

print(FCS_Palpha$total)

## summary puberty
summary(db$FCS_PAvg)
sd(db$FCS_PAvg, na.rm = TRUE)

## scoring now
db[, FCS_CAvg := rowMeans(.SD, na.rm = TRUE), .SDcols = c("FCS.3.2_1", "FCS.3.2_2", "FCS.3.2_3", "FCS.3.2_4", "FCS.3.2_5")]

## current alpha
FCS_Calpha <- alpha(db[, c("FCS.3.2_1", "FCS.3.2_2", "FCS.3.2_3", "FCS.3.2_4", "FCS.3.2_5")])

print(FCS_Calpha$total)

## summary puberty
summary(db$FCS_CAvg)
sd(db$FCS_CAvg, na.rm = TRUE)
```

# EDS
```{r}

db[, EDS_Total := rowMeans(.SD, na.rm = TRUE)*9,
     .SDcols = c("EDS.1_1", "EDS.1_2", "EDS.1_3", "EDS.1_4", "EDS.1_5", "EDS.1_6", "EDS.1_7", "EDS.1_8", "EDS.1_9")]

## alpha
EDS_alpha <- alpha(db[, c("EDS.1_1", "EDS.1_2", "EDS.1_3", "EDS.1_4", "EDS.1_5", "EDS.1_6", "EDS.1_7", "EDS.1_8", "EDS.1_9")])

print(EDS_alpha$total)

## summary
summary(db$EDS_Total)
sd(db$EDS_Total, na.rm = TRUE)
```

# Blooms Scale
```{r}
## average

db[, BloomS_Average := rowMeans(.SD, na.rm = TRUE),
     .SDcols = c("BloomS_1", "BloomS_2", "BloomS_3", "BloomS_4", "BloomS_5")]

## alpha
BloomS_alpha <- alpha(db[, c("BloomS_1", "BloomS_2", "BloomS_3", "BloomS_4", "BloomS_5")])

print(BloomS_alpha$total)

## summary 
summary(db$BloomS_Average)
sd(db$BloomS_Average, na.rm = TRUE)
```


# PDS
```{r}
## alpha
PDS_alpha <- alpha(db[, c("Retro_PDS.1_1", "Retro_PDS.1_2", "Retro_PDS.1_3", "Retro_PDS.1_4", "Retro_PDS.1_5", "Retro_PDS.1_6", "Retro_PDS.1_7")]) 

print(PDS_alpha$total)

## sum scores
db[, PDS_Sum := rowMeans(.SD, na.rm = TRUE)*7,
     .SDcols = c("Retro_PDS.1_1", "Retro_PDS.1_2", "Retro_PDS.1_3", "Retro_PDS.1_4", "Retro_PDS.1_5", "Retro_PDS.1_6", "Retro_PDS.1_7")]

## summary 
summary(db$PDS_Sum)
sd(db$PDS_Sum, na.rm = TRUE)

```


# CTQ
```{r}

## reversal (using toris as a guide)

db[, CTQ.1_2 := (6 - CTQ.1_2)]
db[, CTQ.1_5 := (6 - CTQ.1_5)]
db[, CTQ.1_7 := (6 - CTQ.1_7)]
db[, CTQ.1_10 := (6 - CTQ.1_10)]
db[, CTQ.1_13 := (6 - CTQ.1_13)]
db[, CTQ.1_16 := (6 - CTQ.1_16)]
db[, CTQ.1_19 := (6 - CTQ.1_19)]
db[, CTQ.1_22 := (6 - CTQ.1_22)]
db[, CTQ.1_26 := (6 - CTQ.1_26)]
db[, CTQ.1_28 := (6 - CTQ.1_28)]

## alpha
CTQ_alpha <- alpha(db[, c("CTQ.1_1", "CTQ.1_2", "CTQ.1_3", "CTQ.1_4", "CTQ.1_5", "CTQ.1_6", "CTQ.1_7", "CTQ.1_8", "CTQ.1_9", "CTQ.1_10", "CTQ.1_11", "CTQ.1_12", "CTQ.1_13", "CTQ.1_14","CTQ.1_15", "CTQ.1_16", "CTQ.1_17", "CTQ.1_18", "CTQ.1_19", "CTQ.1_20", "CTQ.1_21", "CTQ.1_22", "CTQ.1_23", "CTQ.1_24", "CTQ.1_25", "CTQ.1_26", "CTQ.1_27", "CTQ.1_28", "CTQ.1_29", "CTQ.1_30", "CTQ.1_31", "CTQ.1_32")])

print(CTQ_alpha$total)

## emotional abuse (using toris calculations)

db[, CTQ_EmotionAbuse := rowMeans(.SD, na.rm = TRUE)*5,
     .SDcols = c("CTQ.1_3", "CTQ.1_8", "CTQ.1_14", "CTQ.1_18", "CTQ.1_25")]
summary(db$CTQ_EmotionAbuse)
sd(db$CTQ_EmotionAbuse, na.rm = TRUE)

## physical abuse

db[, CTQ_PhysicalAbuse := rowMeans(.SD, na.rm = TRUE)*5,
     .SDcols = c("CTQ.1_9", "CTQ.1_11", "CTQ.1_12", "CTQ.1_15", "CTQ.1_17")]
summary(db$CTQ_PhysicalAbuse)
sd(db$CTQ_PhysicalAbuse, na.rm = TRUE)

## sexual abuse

db[, CTQ_SexAbuse := rowMeans(.SD, na.rm = TRUE)*5,
     .SDcols = c("CTQ.1_20", "CTQ.1_21", "CTQ.1_23", "CTQ.1_24", "CTQ.1_27")]
summary(db$CTQ_SexAbuse)
sd(db$CTQ_SexAbuse, na.rm = TRUE)

## emotional neglect

db[, CTQ_EmotionNeglect := rowMeans(.SD, na.rm = TRUE)*5,
     .SDcols = c("CTQ.1_5", "CTQ.1_7", "CTQ.1_13", "CTQ.1_19", "CTQ.1_28")]
summary(db$CTQ_EmotionNeglect)
sd(db$CTQ_EmotionNeglect, na.rm = TRUE)
## physical neglect

db[, CTQ_PhysicalNeglect := rowMeans(.SD, na.rm = TRUE)*5,
     .SDcols = c("CTQ.1_1", "CTQ.1_2", "CTQ.1_4", "CTQ.1_6", "CTQ.1_26")]
summary(db$CTQ_PhysicalNeglect)
sd(db$CTQ_PhysicalNeglect, na.rm = TRUE)

## minimisation

db[, CTQ_Minimise := rowMeans(.SD, na.rm = TRUE)*3,
     .SDcols = c("CTQ.1_10", "CTQ.1_16", "CTQ.1_22")]
summary(db$CTQ_Minimise)
sd(db$CTQ_Minimise, na.rm = TRUE)

```

# DHEQ Preface

The DHEQ has been scored in 4 different ways to reflect methods in current literature. The have been labelled here as versions 1 to 4. More information can be found in the codebook.

Version 1: Responses are not recorded to allow for differentiation on a continuous scale including whether discrimination occurred or did not occur. A mean is then computed for responses to all items, indicating the mean level of distress the respondent feels related to these experiences.

Version 2: Responses are recoded so that 0 = 0, discrimination did not happen, and 1-5 = 1, discrimination did happen (regardless of the degree it bothered the respondent). Items are then summed for a total score indicating how many of these experiences participants have had.

Version 3: Responses are recoded so that 0 and 1 = 1 (did not bother) and the rest of the responses remain the same. A mean is then computed for responses to all items, indicating the mean level of distress the respondent feels related to these experiences.

Version 4: Responses are recoded so that 0 and 1 = 0, discrimination did not happen, and 2-5 = 1, discrimination did happen. Items are then summed for a total score indicating how many of these experiences participants have had.

```{r}
## recoding so that the responses are 0-5 rather than 1-6 
cols <- c("DHEQ_GE.Puberty_1", "DHEQ_GE.Puberty_2", "DHEQ_GE.Puberty_3", "DHEQ_GE.Puberty_4", "DHEQ_GE.Puberty_5", "DHEQ_GE.Puberty_6", "DHEQ_HD.Puberty_1", "DHEQ_HD.Puberty_2", "DHEQ_HD.Puberty_3", "DHEQ_HD.Puberty_4", "DHEQ_HD.Puberty_5", "DHEQ_HD.Puberty_6", "DHEQ_Vic.Puberty_1", "DHEQ_Vic.Puberty_2", "DHEQ_Vic.Puberty_3", "DHEQ_Vic.Puberty_4", "DHEQ_Vig.Puberty_1", "DHEQ_Vig.Puberty_2", "DHEQ_Vig.Puberty_3", "DHEQ_Vig.Puberty_4", "DHEQ_Vig.Puberty_5", "DHEQ_Vig.Puberty_6", "DHEQ_FO.Puberty_1", "DHEQ_FO.Puberty_2", "DHEQ_FO.Puberty_3", "DHEQ_FO.Puberty_4", "DHEQ_FO.Puberty_5", "DHEQ_FO.Puberty_6", "DHEQ_VT.Puberty_1", "DHEQ_VT.Puberty_2", "DHEQ_VT.Puberty_3", "DHEQ_VT.Puberty_4", "DHEQ_VT.Puberty_5", "DHEQ_VT.Puberty_6", "DHEQ_I.Puberty_1", "DHEQ_I.Puberty_2", "DHEQ_I.Puberty_3", "DHEQ_I.Puberty_4")

db[, (cols) := lapply(.SD, function(x) x - 1), .SDcols = cols]

## DHEQ alpha
DHEQ_alpha <- alpha(db[, c("DHEQ_GE.Puberty_1", "DHEQ_GE.Puberty_2", "DHEQ_GE.Puberty_3", "DHEQ_GE.Puberty_4", "DHEQ_GE.Puberty_5", "DHEQ_GE.Puberty_6", "DHEQ_HD.Puberty_1", "DHEQ_HD.Puberty_2", "DHEQ_HD.Puberty_3", "DHEQ_HD.Puberty_4", "DHEQ_HD.Puberty_5", "DHEQ_HD.Puberty_6", "DHEQ_Vic.Puberty_1", "DHEQ_Vic.Puberty_2", "DHEQ_Vic.Puberty_3", "DHEQ_Vic.Puberty_4", "DHEQ_Vig.Puberty_1", "DHEQ_Vig.Puberty_2", "DHEQ_Vig.Puberty_3", "DHEQ_Vig.Puberty_4", "DHEQ_Vig.Puberty_5", "DHEQ_Vig.Puberty_6", "DHEQ_FO.Puberty_1", "DHEQ_FO.Puberty_2", "DHEQ_FO.Puberty_3", "DHEQ_FO.Puberty_4", "DHEQ_FO.Puberty_5", "DHEQ_FO.Puberty_6", "DHEQ_VT.Puberty_1", "DHEQ_VT.Puberty_2", "DHEQ_VT.Puberty_3", "DHEQ_VT.Puberty_4", "DHEQ_VT.Puberty_5", "DHEQ_VT.Puberty_6", "DHEQ_I.Puberty_1", "DHEQ_I.Puberty_2", "DHEQ_I.Puberty_3", "DHEQ_I.Puberty_4")])

print(DHEQ_alpha$total)
```


## DHEQ Version 1
```{r}
## Gender expression average
db[, DHEQ_V1_GE_Avg := rowMeans(.SD, na.rm = TRUE),
     .SDcols = c("DHEQ_GE.Puberty_1", "DHEQ_GE.Puberty_2", "DHEQ_GE.Puberty_3", "DHEQ_GE.Puberty_4", "DHEQ_GE.Puberty_5", "DHEQ_GE.Puberty_6")]
summary(db$DHEQ_V1_GE_Avg)
sd(db$DHEQ_V1_GE_Avg, na.rm = TRUE)

DHEQ_GE_alpha <- alpha(db[, c("DHEQ_GE.Puberty_1", "DHEQ_GE.Puberty_2", "DHEQ_GE.Puberty_3", "DHEQ_GE.Puberty_4", "DHEQ_GE.Puberty_5", "DHEQ_GE.Puberty_6")])
print(DHEQ_GE_alpha$total)

## Harassment and discrimination average
db[, DHEQ_V1_HD_Avg := rowMeans(.SD, na.rm = TRUE),
     .SDcols = c("DHEQ_HD.Puberty_1", "DHEQ_HD.Puberty_2", "DHEQ_HD.Puberty_3", "DHEQ_HD.Puberty_4", "DHEQ_HD.Puberty_5", "DHEQ_HD.Puberty_6")]
summary(db$DHEQ_V1_HD_Avg)
sd(db$DHEQ_V1_HD_Avg, na.rm = TRUE)

DHEQ_HD_alpha <- alpha(db[, c("DHEQ_HD.Puberty_1", "DHEQ_HD.Puberty_2", "DHEQ_HD.Puberty_3", "DHEQ_HD.Puberty_4", "DHEQ_HD.Puberty_5", "DHEQ_HD.Puberty_6")])
print(DHEQ_HD_alpha$total)

## Victimization average
db[, DHEQ_V1_Vic_Avg := rowMeans(.SD, na.rm = TRUE),
     .SDcols = c("DHEQ_Vic.Puberty_1", "DHEQ_Vic.Puberty_2", "DHEQ_Vic.Puberty_3", "DHEQ_Vic.Puberty_4")]
summary(db$DHEQ_V1_Vic_Avg)
sd(db$DHEQ_V1_Vic_Avg, na.rm = TRUE)

DHEQ_Vic_alpha <- alpha(db[, c("DHEQ_Vic.Puberty_1", "DHEQ_Vic.Puberty_2", "DHEQ_Vic.Puberty_3", "DHEQ_Vic.Puberty_4")])
print(DHEQ_Vic_alpha$total)

## Vigilance average
db[, DHEQ_V1_Vig_Avg := rowMeans(.SD, na.rm = TRUE),
     .SDcols = c("DHEQ_Vig.Puberty_1", "DHEQ_Vig.Puberty_2", "DHEQ_Vig.Puberty_3", "DHEQ_Vig.Puberty_4", "DHEQ_Vig.Puberty_5", "DHEQ_Vig.Puberty_6")]
summary(db$DHEQ_V1_Vig_Avg)
sd(db$DHEQ_V1_Vig_Avg, na.rm = TRUE)

DHEQ_Vig_alpha <- alpha(db[, c("DHEQ_Vig.Puberty_1", "DHEQ_Vig.Puberty_2", "DHEQ_Vig.Puberty_3", "DHEQ_Vig.Puberty_4", "DHEQ_Vig.Puberty_5", "DHEQ_Vig.Puberty_6")])
print(DHEQ_Vig_alpha$total)

## Family of origin average
db[, DHEQ_V1_FO_Avg := rowMeans(.SD, na.rm = TRUE),
     .SDcols = c("DHEQ_FO.Puberty_1", "DHEQ_FO.Puberty_2", "DHEQ_FO.Puberty_3", "DHEQ_FO.Puberty_4", "DHEQ_FO.Puberty_5", "DHEQ_FO.Puberty_6")]
summary(db$DHEQ_V1_FO_Avg)
sd(db$DHEQ_V1_FO_Avg, na.rm = TRUE)

DHEQ_FO_alpha <- alpha(db[, c("DHEQ_FO.Puberty_1", "DHEQ_FO.Puberty_2", "DHEQ_FO.Puberty_3", "DHEQ_FO.Puberty_4", "DHEQ_FO.Puberty_5", "DHEQ_FO.Puberty_6")])
print(DHEQ_FO_alpha$total)

## Vicarious trauma average
db[, DHEQ_V1_VT_Avg := rowMeans(.SD, na.rm = TRUE),
     .SDcols = c("DHEQ_VT.Puberty_1", "DHEQ_VT.Puberty_2", "DHEQ_VT.Puberty_3", "DHEQ_VT.Puberty_4", "DHEQ_VT.Puberty_5", "DHEQ_VT.Puberty_6")]
summary(db$DHEQ_V1_VT_Avg)
sd(db$DHEQ_V1_VT_Avg, na.rm = TRUE)

DHEQ_VT_alpha <- alpha(db[, c("DHEQ_VT.Puberty_1", "DHEQ_VT.Puberty_2", "DHEQ_VT.Puberty_3", "DHEQ_VT.Puberty_4", "DHEQ_VT.Puberty_5", "DHEQ_VT.Puberty_6")])
print(DHEQ_VT_alpha$total)

## Isolation average
db[, DHEQ_V1_I_Avg := rowMeans(.SD, na.rm = TRUE),
     .SDcols = c("DHEQ_I.Puberty_1", "DHEQ_I.Puberty_2", "DHEQ_I.Puberty_3", "DHEQ_I.Puberty_4")]
summary(db$DHEQ_V1_I_Avg)
sd(db$DHEQ_V1_I_Avg, na.rm = TRUE)

DHEQ_I_alpha <- alpha(db[, c("DHEQ_I.Puberty_1", "DHEQ_I.Puberty_2", "DHEQ_I.Puberty_3", "DHEQ_I.Puberty_4")])
print(DHEQ_I_alpha$total)

```


## DHEQ Version 2

```{r}
## create new db for this version
dbv2 <- db

## Recode new columns where 0 = 0 and 1 - 5 = 1
vars <- c("DHEQ_GE.Puberty_1", "DHEQ_GE.Puberty_2", "DHEQ_GE.Puberty_3", "DHEQ_GE.Puberty_4", "DHEQ_GE.Puberty_5", "DHEQ_GE.Puberty_6",
          "DHEQ_HD.Puberty_1", "DHEQ_HD.Puberty_2", "DHEQ_HD.Puberty_3", "DHEQ_HD.Puberty_4", "DHEQ_HD.Puberty_5", "DHEQ_HD.Puberty_6",
          "DHEQ_Vic.Puberty_1", "DHEQ_Vic.Puberty_2", "DHEQ_Vic.Puberty_3", "DHEQ_Vic.Puberty_4",
          "DHEQ_Vig.Puberty_1", "DHEQ_Vig.Puberty_2", "DHEQ_Vig.Puberty_3", "DHEQ_Vig.Puberty_4", "DHEQ_Vig.Puberty_5", "DHEQ_Vig.Puberty_6",
          "DHEQ_FO.Puberty_1", "DHEQ_FO.Puberty_2", "DHEQ_FO.Puberty_3", "DHEQ_FO.Puberty_4", "DHEQ_FO.Puberty_5", "DHEQ_FO.Puberty_6",
          "DHEQ_VT.Puberty_1", "DHEQ_VT.Puberty_2", "DHEQ_VT.Puberty_3", "DHEQ_VT.Puberty_4", "DHEQ_VT.Puberty_5", "DHEQ_VT.Puberty_6",
          "DHEQ_I.Puberty_1", "DHEQ_I.Puberty_2", "DHEQ_I.Puberty_3", "DHEQ_I.Puberty_4")

dbv2[, (vars) := lapply(.SD, function(x) as.numeric(as.character(x))), .SDcols = vars]

dbv2[, (vars) := lapply(.SD, function(x) ifelse(x == 0, 0, 1)), .SDcols = vars]

## Gender expression sum
dbv2[, DHEQ_V2_GE_sum := rowMeans(.SD, na.rm = TRUE)*6,
     .SDcols = c("DHEQ_GE.Puberty_1", "DHEQ_GE.Puberty_2", "DHEQ_GE.Puberty_3", "DHEQ_GE.Puberty_4", "DHEQ_GE.Puberty_5", "DHEQ_GE.Puberty_6")]

## Harassment and discrimination sum
dbv2[, DHEQ_V2_HD_sum := rowMeans(.SD, na.rm = TRUE)*6,
     .SDcols = c("DHEQ_HD.Puberty_1", "DHEQ_HD.Puberty_2", "DHEQ_HD.Puberty_3", "DHEQ_HD.Puberty_4", "DHEQ_HD.Puberty_5", "DHEQ_HD.Puberty_6")]

## Victimization sum
dbv2[, DHEQ_V2_Vic_sum := rowMeans(.SD, na.rm = TRUE)*4,
     .SDcols = c("DHEQ_Vic.Puberty_1", "DHEQ_Vic.Puberty_2", "DHEQ_Vic.Puberty_3", "DHEQ_Vic.Puberty_4")]

## Vigilance sum
dbv2[, DHEQ_V2_Vig_sum := rowMeans(.SD, na.rm = TRUE)*6,
     .SDcols = c("DHEQ_Vig.Puberty_1", "DHEQ_Vig.Puberty_2", "DHEQ_Vig.Puberty_3", "DHEQ_Vig.Puberty_4", "DHEQ_Vig.Puberty_5", "DHEQ_Vig.Puberty_6")]

## Family of origin sum
dbv2[, DHEQ_V2_FO_sum := rowMeans(.SD, na.rm = TRUE)*6,
     .SDcols = c("DHEQ_FO.Puberty_1", "DHEQ_FO.Puberty_2", "DHEQ_FO.Puberty_3", "DHEQ_FO.Puberty_4", "DHEQ_FO.Puberty_5", "DHEQ_FO.Puberty_6")]

## Vicarious trauma sum
dbv2[, DHEQ_V2_VT_sum := rowMeans(.SD, na.rm = TRUE)*6,
     .SDcols = c("DHEQ_VT.Puberty_1", "DHEQ_VT.Puberty_2", "DHEQ_VT.Puberty_3", "DHEQ_VT.Puberty_4", "DHEQ_VT.Puberty_5", "DHEQ_VT.Puberty_6")]

## Isolation sum
dbv2[, DHEQ_V2_I_sum := rowMeans(.SD, na.rm = TRUE)*4,
     .SDcols = c("DHEQ_I.Puberty_1", "DHEQ_I.Puberty_2", "DHEQ_I.Puberty_3", "DHEQ_I.Puberty_4")]


```

## DHEQ Version 3
```{r}
## Create new db for this version
dbv3 <- db

## making zero equal one

vars <- c("DHEQ_GE.Puberty_1", "DHEQ_GE.Puberty_2", "DHEQ_GE.Puberty_3", "DHEQ_GE.Puberty_4", "DHEQ_GE.Puberty_5", "DHEQ_GE.Puberty_6",
          "DHEQ_HD.Puberty_1", "DHEQ_HD.Puberty_2", "DHEQ_HD.Puberty_3", "DHEQ_HD.Puberty_4", "DHEQ_HD.Puberty_5", "DHEQ_HD.Puberty_6",
          "DHEQ_Vic.Puberty_1", "DHEQ_Vic.Puberty_2", "DHEQ_Vic.Puberty_3", "DHEQ_Vic.Puberty_4",
          "DHEQ_Vig.Puberty_1", "DHEQ_Vig.Puberty_2", "DHEQ_Vig.Puberty_3", "DHEQ_Vig.Puberty_4", "DHEQ_Vig.Puberty_5", "DHEQ_Vig.Puberty_6",
          "DHEQ_FO.Puberty_1", "DHEQ_FO.Puberty_2", "DHEQ_FO.Puberty_3", "DHEQ_FO.Puberty_4", "DHEQ_FO.Puberty_5", "DHEQ_FO.Puberty_6",
          "DHEQ_VT.Puberty_1", "DHEQ_VT.Puberty_2", "DHEQ_VT.Puberty_3", "DHEQ_VT.Puberty_4", "DHEQ_VT.Puberty_5", "DHEQ_VT.Puberty_6",
          "DHEQ_I.Puberty_1", "DHEQ_I.Puberty_2", "DHEQ_I.Puberty_3", "DHEQ_I.Puberty_4")

dbv3[, (vars) := lapply(.SD, function(x) as.numeric(as.character(x))), .SDcols = vars]

dbv3[, (vars) := lapply(.SD, function(x) ifelse(x == 0, 1, x)), .SDcols = vars]

## Gender expression average
dbv3[, DHEQ_V3_GE_Avg := rowMeans(.SD, na.rm = TRUE),
     .SDcols = c("DHEQ_GE.Puberty_1", "DHEQ_GE.Puberty_2", "DHEQ_GE.Puberty_3", "DHEQ_GE.Puberty_4", "DHEQ_GE.Puberty_5", "DHEQ_GE.Puberty_6")]

## Harassment and discrimination average
dbv3[, DHEQ_V3_HD_Avg := rowMeans(.SD, na.rm = TRUE),
     .SDcols = c("DHEQ_HD.Puberty_1", "DHEQ_HD.Puberty_2", "DHEQ_HD.Puberty_3", "DHEQ_HD.Puberty_4", "DHEQ_HD.Puberty_5", "DHEQ_HD.Puberty_6")]

# Victimization average
dbv3[, DHEQ_V3_Vic_Avg := rowMeans(.SD, na.rm = TRUE),
     .SDcols = c("DHEQ_Vic.Puberty_1", "DHEQ_Vic.Puberty_2", "DHEQ_Vic.Puberty_3", "DHEQ_Vic.Puberty_4")]

# Vigilance average
dbv3[, DHEQ_V3_Vig_Avg := rowMeans(.SD, na.rm = TRUE),
     .SDcols = c("DHEQ_Vig.Puberty_1", "DHEQ_Vig.Puberty_2", "DHEQ_Vig.Puberty_3", "DHEQ_Vig.Puberty_4", "DHEQ_Vig.Puberty_5", "DHEQ_Vig.Puberty_6")]

# Family of origin average
dbv3[, DHEQ_V3_FO_Avg := rowMeans(.SD, na.rm = TRUE),
     .SDcols = c("DHEQ_FO.Puberty_1", "DHEQ_FO.Puberty_2", "DHEQ_FO.Puberty_3", "DHEQ_FO.Puberty_4", "DHEQ_FO.Puberty_5", "DHEQ_FO.Puberty_6")]

# Vicarious trauma average
dbv3[, DHEQ_V3_VT_Avg := rowMeans(.SD, na.rm = TRUE),
     .SDcols = c("DHEQ_VT.Puberty_1", "DHEQ_VT.Puberty_2", "DHEQ_VT.Puberty_3", "DHEQ_VT.Puberty_4", "DHEQ_VT.Puberty_5", "DHEQ_VT.Puberty_6")]

# Isolation average
dbv3[, DHEQ_V3_I_Avg := rowMeans(.SD, na.rm = TRUE),
     .SDcols = c("DHEQ_I.Puberty_1", "DHEQ_I.Puberty_2", "DHEQ_I.Puberty_3", "DHEQ_I.Puberty_4")]

```

## DHEQ Version 4
```{r}
## Create new db for this version
dbv4 <- db

## making zero and one equal zero, and two through five equal one
vars <- c("DHEQ_GE.Puberty_1", "DHEQ_GE.Puberty_2", "DHEQ_GE.Puberty_3", "DHEQ_GE.Puberty_4", "DHEQ_GE.Puberty_5", "DHEQ_GE.Puberty_6",
          "DHEQ_HD.Puberty_1", "DHEQ_HD.Puberty_2", "DHEQ_HD.Puberty_3", "DHEQ_HD.Puberty_4", "DHEQ_HD.Puberty_5", "DHEQ_HD.Puberty_6",
          "DHEQ_Vic.Puberty_1", "DHEQ_Vic.Puberty_2", "DHEQ_Vic.Puberty_3", "DHEQ_Vic.Puberty_4",
          "DHEQ_Vig.Puberty_1", "DHEQ_Vig.Puberty_2", "DHEQ_Vig.Puberty_3", "DHEQ_Vig.Puberty_4", "DHEQ_Vig.Puberty_5", "DHEQ_Vig.Puberty_6",
          "DHEQ_FO.Puberty_1", "DHEQ_FO.Puberty_2", "DHEQ_FO.Puberty_3", "DHEQ_FO.Puberty_4", "DHEQ_FO.Puberty_5", "DHEQ_FO.Puberty_6",
          "DHEQ_VT.Puberty_1", "DHEQ_VT.Puberty_2", "DHEQ_VT.Puberty_3", "DHEQ_VT.Puberty_4", "DHEQ_VT.Puberty_5", "DHEQ_VT.Puberty_6",
          "DHEQ_I.Puberty_1", "DHEQ_I.Puberty_2", "DHEQ_I.Puberty_3", "DHEQ_I.Puberty_4")

dbv4[, (vars) := lapply(.SD, function(x) as.numeric(as.character(x))), .SDcols = vars]

dbv4[, (vars) := lapply(.SD, function(x) ifelse(x <= 1, 0, 1)), .SDcols = vars]

## Gender expression sum
dbv4[, DHEQ_V4_GE_sum := rowMeans(.SD, na.rm = TRUE)*6,
     .SDcols = c("DHEQ_GE.Puberty_1", "DHEQ_GE.Puberty_2", "DHEQ_GE.Puberty_3", "DHEQ_GE.Puberty_4", "DHEQ_GE.Puberty_5", "DHEQ_GE.Puberty_6")]
summary(dbv4$DHEQ_V4_GE_sum)
sd(dbv4$DHEQ_V4_GE_sum, na.rm = TRUE)

## Harassment and discrimination sum
dbv4[, DHEQ_V4_HD_sum := rowMeans(.SD, na.rm = TRUE)*6,
     .SDcols = c("DHEQ_HD.Puberty_1", "DHEQ_HD.Puberty_2", "DHEQ_HD.Puberty_3", "DHEQ_HD.Puberty_4", "DHEQ_HD.Puberty_5", "DHEQ_HD.Puberty_6")]
summary(dbv4$DHEQ_V4_HD_sum)
sd(dbv4$DHEQ_V4_HD_sum, na.rm = TRUE)

## Victimization sum
dbv4[, DHEQ_V4_Vic_sum := rowMeans(.SD, na.rm = TRUE)*4,
     .SDcols = c("DHEQ_Vic.Puberty_1", "DHEQ_Vic.Puberty_2", "DHEQ_Vic.Puberty_3", "DHEQ_Vic.Puberty_4")]
summary(dbv4$DHEQ_V4_Vic_sum)
sd(dbv4$DHEQ_V4_Vic_sum, na.rm = TRUE)

## Vigilance sum
dbv4[, DHEQ_V4_Vig_sum := rowMeans(.SD, na.rm = TRUE)*6,
     .SDcols = c("DHEQ_Vig.Puberty_1", "DHEQ_Vig.Puberty_2", "DHEQ_Vig.Puberty_3", "DHEQ_Vig.Puberty_4", "DHEQ_Vig.Puberty_5", "DHEQ_Vig.Puberty_6")]
summary(dbv4$DHEQ_V4_Vig_sum)
sd(dbv4$DHEQ_V4_Vig_sum, na.rm = TRUE)

## Family of origin sum
dbv4[, DHEQ_V4_FO_sum := rowMeans(.SD, na.rm = TRUE)*6,
     .SDcols = c("DHEQ_FO.Puberty_1", "DHEQ_FO.Puberty_2", "DHEQ_FO.Puberty_3", "DHEQ_FO.Puberty_4", "DHEQ_FO.Puberty_5", "DHEQ_FO.Puberty_6")]
summary(dbv4$DHEQ_V4_FO_sum)
sd(dbv4$DHEQ_V4_FO_sum, na.rm = TRUE)

## Vicarious trauma sum
dbv4[, DHEQ_V4_VT_sum := rowMeans(.SD, na.rm = TRUE)*6,
     .SDcols = c("DHEQ_VT.Puberty_1", "DHEQ_VT.Puberty_2", "DHEQ_VT.Puberty_3", "DHEQ_VT.Puberty_4", "DHEQ_VT.Puberty_5", "DHEQ_VT.Puberty_6")]
summary(dbv4$DHEQ_V4_VT_sum)
sd(dbv4$DHEQ_V4_VT_sum, na.rm = TRUE)

## Isolation sum
dbv4[, DHEQ_V4_I_sum := rowMeans(.SD, na.rm = TRUE)*4,
     .SDcols = c("DHEQ_I.Puberty_1", "DHEQ_I.Puberty_2", "DHEQ_I.Puberty_3", "DHEQ_I.Puberty_4")]

```

# YASB 
```{r}
## reversal 
db[, YASB_3 := (6 - YASB_3)]
db[, YASB_6 := (6 - YASB_6)]
db[, YASB_10 := (6 - YASB_10)]
db[, YASB_14 := (6 - YASB_14)]

## alpha
YASB_alpha <- alpha(db[, c("YASB_1", "YASB_2", "YASB_3", "YASB_4", "YASB_5", "YASB_6", "YASB_7", "YASB_8", "YASB_9", "YASB_10", "YASB_11", "YASB_12", "YASB_13", "YASB_14")]) 

print(YASB_alpha$total)

## relational aggression total (sum)
db[, YASB_RelAg := rowMeans(.SD, na.rm = TRUE)*5,
     .SDcols = c("YASB_1", "YASB_2", "YASB_9", "YASB_11", "YASB_13")]
summary(db$YASB_RelAg)
sd(db$YASB_RelAg, na.rm = TRUE)

## social aggression total (sum)
db[, YASB_SocAg := rowMeans(.SD, na.rm = TRUE)*5,
     .SDcols = c("YASB_4", "YASB_5", "YASB_7", "YASB_8", "YASB_12")]
summary(db$YASB_SocAg)
sd(db$YASB_SocAg, na.rm = TRUE)

## interpersonal maturity total (sum)
db[, YASB_Mat := rowMeans(.SD, na.rm = TRUE)*4,
     .SDcols = c("YASB_3", "YASB_6", "YASB_10", "YASB_14")]
summary(db$YASB_Mat)
sd(db$YASB_Mat, na.rm = TRUE)

```
## NaN to NA

```{r}
db$x1[is.nan(db$x1)]<-NA
```

